\disstitle

### 2018-06-16 chapters/introduction/introduction.tex
first paragraph

\brief{
The topic of understanding images has been around for half a century.
A well known [annodose] in computer vision community is set in the
60s. The MIT professor Dr. Marvin Minsky assigned a couple of
undergrads to spend the summer programming a computer to recognize
objects in the scene~\cite{boden2006mind}. Quite like the attempts of
proving the famous ``Four color theorem'', [[story about a prof claim
he can prove it in a class]]. Fortunate for the mathematicans, the
``Four color theorem'' has been proved by using powerful computational
resources, while the computer scientists are still trapped in Dr.
Marvin Minsky's summer program (not fully solved yet).
}

>>>>

The study of understanding images has been around for half a century.
A well known anecdote in computer vision community happened in 1960s,
when the MIT professor Dr. Marvin Minsky assigned a summer programming
project to his undergraduates, to recognize objects in a
scene~\cite{boden2006mind}. 
%
Similar to the story of the famous ``Four Color Conjecture'', where
one of the world's renowned mathematicians Dr. Hermann Minkowski
claimed in his class that he was able to solve it before the class
ends.  
However, Not until one hundred years later since it was first
proposed, the ``Four Color Conjecture'' has been stamped as theorem by
the continuous efforts of several generations of talented
mathematicians.  While on the other side, Dr. Marvin Minsky's summer
program still remains open.
